% !TEX root =  ../report.tex
\section{RESULTS}
\indent The received reviews from the evaluators were summarized into problems and later improvement areas. These areas are meant to streamline the process of incorporating the received feedback in the development of the app. It has been shown that there are several issues with the current state of the application, regarding both its design and functionality.
\newline
\newline
Problem 1.
\newline
The board page is too full, all the lists and buttons make the space very tight. It is difficult and somewhat counter-intuitive to navigate through the board without feeling overwhelmed.
\newline
Related Heuristics: 8
\newline
\indent In the board overview page, the app currently has many functional elements in the same space, which to the novice user can be overwhelming. It might lead to confusion in cases where an element's functionality is not immediately obvious, and overall degrades the user experience.
\newline
"[it is] Difficult to navigate and use the board effectively without it seeming overbearing"\cite{team-review}
\newline
\indent The resolution of this problem is a high priority since the user is likely to spend most of their time using the app on the board overview page. As the heart of the application, it is critical that the user experience is best here, with minimal friction in the common user actions.
\newline
\newline
Problem 2.
\newline
The purpose of board keys in the app is inadequately explained by the time the user is required to enter one, and if they don't understand how board keys work they will miss out on the app's features.
\newline
Related Heuristics: 4, 6, 10
\newline
\indent About 50\% of the evaluators found that the application’s approach to joining a board using a board key may prove difficult for users unfamiliar with the system. It is not made clear how board keys work, and that information is not available anywhere in the app. 
\newline
\indent The frequency of this problem alongside the fact that it is a crucial feature of the app will prioritise its resolution.
\newline
\newline
Problem 3.
\newline
The Landing Page does not reflect the actual application's use and is unclear what each button is for.
\newline
Related Heuristics: 8, 10
\newline
\indent The Landing Page is confusing for new users since it is nowhere specified what the options "public", "team" and "private" actually mean and do. We encountered the frequency to be about 17\%, but even so, the problem is severe, since it affects the ease of use of the app, more so because the Landing Page is the entry point of the application.
\newline
\newline
Problem 4.
\newline
The application's color customisation options are user-unfriendly.
\newline
Related Heuristics: 6, 7
\newline
\indent The application is customisable enough to let the user change their board theme and colors, but when the user enters the color they want for their board in the specified text field, there is no way to preview how the board will look with that color. Besides that, there is no default color palette anywhere in the app, requiring a user to memorise the board's colors (for example, when choosing a color for a new tag).
\newline
\indent This issue is not impeding the app's functionality and thus will be below others in priority, but will also be taken into account and eventually resolved.
\newline
\newline
Problem 5.
\newline
Adding a new list to the board on the overview page is unintuitive, and the related button is hard to reach.
\newline
Related Heuristics: 6,8
\newline
\indent The reviewers found the position of the add list button to be inappropriate (located at the end of the horizontally scrollable view of lists, on the right side of the board). 
\newline
\indent This issue is of low severity, and can be easily resolved.
\newline
\newline
Problem 6. 
\newline
Incomprehensive password requirement field on board creation page.
\newline
Related Heuristics: 8
\newline
\indent On the Board Creation Overview page, there is a password text field along with a "password required" radio button. Although it is logical to assume that leaving the password field empty means there is no password for the board, the radio button was added as an extra precaution in case a user accidentally types something in the password field. However, this extra feature has been deemed unnecessary as it only adds complexity to the scene without providing significant improvement. Additionally, the presence of an asterisk next to the password field suggests that it is a required field, even though it is not. This can cause confusion for users, and as such, it will be fixed.
\newline
\indent Since password protection is essential for the functionality of the app it is important that users can efficiently use it. The issue is of moderate severity, but simple to fix.
\newline
\newline
Problem 7.
\newline
Redundant "Exit" Button on Server Selection window.
\newline
Related Heuristics: 8
\newline
\indent In the design of the Server Selection window, the reviewers found the exit button on the screen to be redundant, since you can exit the app by just closing the window. Having a button on the screen that is not required for the functionality of the application and takes up space makes the screen look cluttered. 
\newline
\indent The problem is of low severity and it is easy to solve since the button can just be deleted and the rest of the screen can be rearranged to adhere to a minimalist design.